\documentclass[11pt,a4paper]{article}

\usepackage[margin=0.7in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{tabularx}

\pagenumbering{gobble}

\hypersetup{
    colorlinks=true,
    urlcolor=blue
}


\titleformat{\section}
{\large\bfseries\color{blue}}
{}
{0em}
{}[\titlerule]


\begin{document}


\begin{center}

{\Huge \textbf{Simran}}\\[6pt]

{\large Computer Science Student | Developer}\\[10pt]


\begin{tabular}{c c}

Email: Koundalsimran41@gmail.com 
&
GitHub: github.com/simran117

\\[6pt]

LinkedIn: linkedin.com/in/simrankoundal
&
Location: Germany

\end{tabular}


\end{center}



\section*{Profile}

Computer Science student with an interest in software development, 
web technologies, and creating innovative solutions. 
Passionate about learning new technologies, improving programming skills,
and developing practical applications to solve real-world problems.



\section*{Education}


\textbf{Bachelor's Degree in Computer Science}

\textit{Gisma University of Applied Sciences}

\hfill 2024 -- 2027


Currently pursuing Computer Science with focus on software development,
programming concepts, databases, and modern technologies.



\vspace{8pt}



\textbf{Upper Secondary Education (Non-Medical - PCM)}

\textit{Nehru Graden School}

\hfill 2023 | 89\%


Completed higher secondary education with Physics, Chemistry, and Mathematics.
Developed analytical thinking, logical reasoning, and problem-solving skills.



\vspace{8pt}



\textbf{Secondary Education}

\textit{Nehru Graden School}

\hfill 2021 | 90\%


Completed secondary education with Science, Mathematics, and Computer fundamentals.
Built a strong foundation in technology and programming concepts.





\section*{Technical Skills}


\begin{tabularx}{\textwidth}{X X}


\textbf{Programming:} 
Python, SQL
&
\textbf{Web:}
HTML5, CSS3


\\[8pt]


\textbf{Database:}
MySQL
&
\textbf{Tools:}
Git, GitHub, VS Code


\end{tabularx}





\section*{Soft Skills}


\begin{itemize}[leftmargin=1.2em]

\item Problem Solving and Analytical Thinking

\item Communication and Team Collaboration

\item Adaptability and Quick Learning

\item Time Management and Creativity

\end{itemize}





\section*{Projects}



\textbf{Guess Game} \hfill \textit{Python}

\begin{itemize}[leftmargin=1.2em]

\item Developed a number guessing game using Python programming concepts,
conditions, and logical implementation.

\end{itemize}




\textbf{Employee Management System} \hfill \textit{SQL}

\begin{itemize}[leftmargin=1.2em]

\item Designed a database system to store, manage, and retrieve employee records efficiently.

\end{itemize}





\textbf{Frontend Website} \hfill \textit{HTML \& CSS}

\begin{itemize}[leftmargin=1.2em]

\item Created a responsive website with structured layouts and modern user interface design.

\end{itemize}





\section*{Declaration}


I hereby declare that the information provided above is true and correct
to the best of my knowledge.



\vfill


\begin{center}

\textbf{Simran}

\end{center}


\end{document}